R package glmm

### 2014-05-22 CompareExamples/glmmexamples.tex
Added salamander example's results

>>>>

\section{Salamander}

\begin{verbatim}
> set.seed(1234)
> sal.glmm3<-glmm(Mate~Cross,random=list(~0+Female,~0+Male),varcomps.names=c("F","M"),data=salamander,family.glmm=bernoulli.glmm,m=10^4)
> summary(sal.glmm3)

Call:
glmm(fixed = Mate ~ Cross, random = list(~0 + Female, ~0 + Male), 
    varcomps.names = c("F", "M"), data = salamander, family.glmm = bernoulli.glmm, 
    m = 10^4)

Fixed Effects:
            Estimate Std. Error z value Pr(>|z|)    
(Intercept)   1.1123     0.2593   4.290 1.79e-05 ***
CrossRW      -0.5545     0.3558  -1.558    0.119    
CrossWR      -3.1701     0.4029  -7.867 3.62e-15 ***
CrossWW      -0.2122     0.3681  -0.577    0.564    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Variance Components for Random Effects (P-values are one-tailed):
  Estimate Std. Error z value Pr(>|z|)/2    
F   1.2087     0.2534   4.769   9.24e-07 ***
M   0.9485     0.1809   5.244   7.86e-08 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Here are the results with $m=10^4$ but I forgot to set the seed.
\begin{verbatim}
> summary(sal.glmm2)

Call:
glmm(fixed = Mate ~ Cross, random = list(~0 + Female, ~0 + Male), 
    varcomps.names = c("F", "M"), data = salamander, family.glmm = bernoulli.glmm, 
    m = 10^4)

Fixed Effects:
            Estimate Std. Error z value Pr(>|z|)    
(Intercept)  0.93879    0.26963   3.482 0.000498 ***
CrossRW     -0.76157    0.37376  -2.038 0.041593 *  
CrossWR     -2.72491    0.40736  -6.689 2.24e-11 ***
CrossWW      0.02256    0.37902   0.060 0.952541    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Variance Components for Random Effects (P-values are one-tailed):
  Estimate Std. Error z value Pr(>|z|)/2    
F   1.5991     0.2965   5.394   3.45e-08 ***
M   0.9908     0.1885   5.255   7.41e-08 ***
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
\end{verbatim}
